A Spatial AR System for Axis-aligned Augmentation of Planar Scenes in Industrial Settings

### 2021-07-10 paper/elsarticle/elsarticle-template.tex
paper

\begin{figure}
    \centering
    \subfloat[\centering Projecting original image.]{{\includegraphics[height=4.2cm]{images/proj_projim.png}}}
    \qquad
    \subfloat[\centering Projecting warped image.]{{\includegraphics[height=4.2cm]{images/proj_projim_waped.png}}}
    \caption{Projection from recovered projector viewpoint (bottom left, black) to scene plane of original image and of warped image. (a) Projecting the original 960~pixel~$\times$~600~pixel image ... (b) After warping the original image accoring to the plane-induced homography for the given target location, the image is projected in a manner that appears ...}
    \label{fig:warp}
\end{figure}

>>>>

\begin{figure}
    \centering
    \subfloat[\centering Projecting original image.]{{\includegraphics[height=4.2cm]{images/proj_projim.png}}}
    \qquad
    \subfloat[\centering Projecting warped image.]{{\includegraphics[height=4.2cm]{images/proj_projim_waped.png}}}
    \caption{Projection from the recovered projector viewpoint (bottom left, black) to the scene plane of the original image and of the warped image. (a) Projecting the original image to the scene plane. (b) After warping the original image according to our plane-induced homography for the given target location, the image is projected in a manner that appears free of perspective distortions, aligned with the axes of the virtual camera, and to have the desired dimensions in the scene plane, expressed in metric units. Note that background in the projected image is shown set to black.}
    \label{fig:warp}
\end{figure}
